---
title: "JLEWIS Final Project"
author: "Jenn Lewis"
date: "2/26/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(gghighlight)
library(tidyverse)
library(dplyr)
library(rio)
library(here)
library(ggrepel)




data1 <- import(here("data", "Full_Data.csv")) 

```



```{r Figure 1}
#Show Heart Rate Data Over Time for Two Groups

#Convert Group to Factor
data1$Group <- as.factor(data1$Group)

data1$Group <- recode(data1$Group, '1' = "Control Group", '2' = "BPD Group")

#Clean Data to proper format
HRV1 <- data1 %>%
  gather(key = HRV_Segment, value = RSA, RSA_1, RSA_2, RSA_3, RSA_4, RSA_5, RSA_6, RSA_7, RSA_8, na.rm =TRUE) %>%
  select(HRV_Segment, RSA, Group) %>%
  filter(Group != "NA") %>%
  group_by(Group, HRV_Segment) %>%
  summarise(RSA = mean(RSA)) %>%
  mutate(HRV_Segment = recode(HRV_Segment,
                              "RSA_1" = "1",
                              "RSA_2" = "2",
                              "RSA_3" = "3",
                              "RSA_4" = "4",
                              "RSA_5" = "5",
                              "RSA_6" = "6",
                              "RSA_7" = "7",
                              "RSA_8" = "8"))


HRV1 %>%
  ggplot(aes(HRV_Segment, RSA, group = Group)) +
  geom_line(aes(color = Group)) +
  theme_minimal() +
  #ylim(0, 7) +
  labs(y = "HRV",
       x = "Segment",
       title = "HRV across Time for BPD vs Control Group")

```

##TN: 

Jenn, great coding fro cleaing data and niche graph! 
It would be nice to have a little bit more description on what your main goal is for this visualization , but I think I get the main idea. 

A line plot seems to be the best way to show how a variable changes across time - and the lines for the two different groups are easy to identify - however, I tink that there are a couple small changes you could do to make this plot stand out : maybe making the lines a bit thicker and using a different color palette good be great adds to your visualization ! also, if you are trying to highlight the big difference between the two groups at segment 7, maybe you could do that by adding a box around that area? or dots on those picks and a line connecting them? 




```{r Figure 2}
#Convert scores to standardized scores
data1 <- data1 %>%
  mutate(HAMA_C = scale(HAMA, center = TRUE, scale = TRUE),
         PHQ_C = scale(PHQ, center = TRUE, scale = TRUE),
         DERS_C = scale(DERS, center = TRUE, scale = TRUE))

#cleaning data
Symptoms <- data1 %>%
  gather(key = Symptom, value = Score, HAMA_C, PHQ_C, DERS_C, na.rm = TRUE) %>%
  mutate(Symptom = recode(Symptom, 
                           "HAMA_C" = "Anxiety",
                           "PHQ_C" = "Depression",
                           "DERS_C" = "Emotion Dysregulation")) %>%
  group_by(Group, Symptom) %>%
  summarise(Score = mean(Score)) %>%
  filter(Group != "NA")

#TN: coded these variables as factor, otherwise ggplot cannot distiguish the different groups to build the plot

Symptoms$Group<- as.factor(Symptoms$Group)
Symptoms$Symptom<- as.factor(Symptoms$Symptom)
  

#Plot to show Mental Health Profile of Groups
Symptoms %>%
  ggplot(aes(Symptom, Score, fill = Group)) +
  geom_col(position = "dodge") +
  scale_fill_viridis_d() +
  theme_minimal() +
  labs(title = "Mental Health Profiles of Clinical and Non-Clinical Samples",
       x = "Symptom",
       y = "Score (standardized)")

```


##TN: 

This graph looks good!! I can see that is good to show important difference between groups 1 and 2 for different symptoms. 
It would be good to clarify in the plot what groups 1 and 2 are though! 
Also, would there be a way for you to show uncertainty on these different measures (like standard error?) 

```{r Figure 3}

##TN: again, coded Group as factor otherwise I cannot build the plot:

library(magrittr)
data1 %<>%
  filter(Group != "NA")

data1$Group<- as.factor(data1$Group)

ggplot(data1, aes(DERS, ColorWord_Score, color = Group)) +
  geom_point() +
  scale_colour_viridis_d(option = "civdis") +
  geom_smooth(method = "lm", alpha = 0.1) +
  theme_minimal() +
  labs(title = "The Relationship Between Emotion Regulation and Inhibitory Control",
       x = "Emotion Regulation Score (DERS)",
       y = "Inhibitory Control (Stroop Score)")
  


```


##TN: 

this is a nice graph! again, I wish I could know what group 1 and 2 represent ...  